Reducing Linearizability of Priority Queues and More Data Structures to State Reachability

### 2017-04-21 appendix-EPQ.tex
modify

\section{Proof in Section \ref{sec:inductive rules of extended priority queue}}
\label{sec:appendix in section inductive rules of extended priority queue}

@@

Let us model priority queue as an LTS $\textit{LTS}_e = (Q,\Sigma,\rightarrow,q_0)$ as follows:

@@

A path of an LTS is a finite transition sequence $q_0\xrightarrow{\beta_1}q_1\overset{\beta_2}{\longrightarrow}\ldots\overset{\beta_k}{\longrightarrow}q_k$ for $k\geq 0$, where $q_0$ is the initial state of the LTS. A trace of an LTS is a finite sequence $\beta_1 \cdot \beta_2 \cdot \ldots \cdot \beta_k$, where $k \geq 0$ if there exists a path $q_0\overset{\beta_1}{\longrightarrow}q_1\overset{\beta_2}{\longrightarrow}\ldots\overset{\beta_k}{\longrightarrow}q_k$ of the LTS. Let $\textit{PQ}_s$ be the set of traces of $\textit{LTS}_e$. The following lemma states that $\textit{PQ} = \textit{PQ}_s$.

@@

To prove that $\textit{PQ} \subseteq \textit{PQ}_s$, we first prove that $\textit{PQ}_{\neq} \subseteq \textit{PQ}_{s\neq}$ by induction.

\begin{itemize}
\setlength{\itemsep}{0.5pt}
\item[-] It is obvious that $\epsilon \in \textit{PQ}_s$.

\item[-] If $l_1 \in \textit{PQ}_{s\neq}$ and $l_2 \xrightarrow{\textit{PQ}_1} l_1$. Then we need to prove that $l_2 \in \textit{PQ}_s$. We know that $l_1 = u \cdot v \cdot w$, such that $\textit{PQ}_1(u,v,w,p)$ holds, and $l_2 = u \cdot \textit{put}(\textit{itm},p) \cdot v \cdot \textit{rm}(\textit{itm})$.

    Assume that $u = \alpha_1 \cdot \ldots \cdot \alpha_i$, $v = \alpha_{\textit{i+1}} \cdot \ldots \cdot \alpha_j$ and $w = \alpha_{\textit{j+1}} \cdot \ldots \cdot \alpha_m$. Assume that $q_0 \xrightarrow{\alpha_1} q_1 \ldots \xrightarrow{\alpha_i} q_i \xrightarrow{\alpha_{\textit{i+1}}} q_{\textit{i+1}} \ldots  \xrightarrow{\alpha_j} q_j \xrightarrow{\alpha_{\textit{j+1}}} q_{\textit{j+1}} \ldots \xrightarrow{\alpha_m} q_m$ is the path of $l_1$ on $\textit{PQ}_s$. For each $i \leq k \leq j$, let $q'_k$ be the same as $q_k$, except that $q'_k$ maps $p$ into $\textit{item} \cdot l_k$ and $q_k$ maps $\textit{pri}$ into $l_k$ for some finite sequence $l_k$.

    We already know that $q_0 \xrightarrow{\alpha_1} q_1 \ldots \xrightarrow{\alpha_i} q_i$, and it is obvious that $q_i \xrightarrow{\textit{put}(\textit{itm},p)} q'_i$. Since (1) all $\textit{put}$ with priority $p$ is in $u$, and (2) in $u \cdot v$, only items with priority either incomparable, or less, or equal than $p$ is removed, we can see that it is safe to add to each $q_k$ ($1 \leq k \leq j$) with a newest $\textit{itm}$ with priority $p$. Or we can say, $q'_i \xrightarrow{\alpha_{\textit{i+1}}} q'_{\textit{i+1}} \ldots \xrightarrow{\alpha_j} q'_j$ are transitions of $\textit{LTS}_e$. Since $\textit{matched}_{\prec}(u \cdot v,p)$ holds, we can see that $q_j$ maps each priority that is smaller than $p$ into $\epsilon$ and maps $p$ into $\epsilon$, and $q'_j$ maps each priority that is smaller than $p$ into $\epsilon$ and maps $p$ into $\textit{itm}$. Then, we can see that $q'_j \xrightarrow{\textit{rm}(\textit{itm})} q_j$. We already know that that $q_j \xrightarrow{\alpha_{\textit{j+1}}} q_{\textit{j+1}} \ldots \xrightarrow{\alpha_m} q_m$. Therefore, we can see that $l_2 = u \cdot \textit{put}(\textit{itm},p) \cdot v \cdot \textit{rm}(\textit{itm}) \in \textit{PQ}_s$.

\item[-] If $l_1 \in \textit{PQ}_{s\neq}$ and $l_2 \xrightarrow{\textit{PQ}_2} l_1$. Then we need to prove that $l_2 \in \textit{PQ}_s$. We know that $l_1 = u \cdot v$, such that $\textit{PQ}_2(u,v,p)$ holds, and $l_2 = u \cdot \textit{put}(\textit{itm},p) \cdot v$.

    Assume that $u = \alpha_1 \cdot \ldots \cdot \alpha_i$ and $v = \alpha_{\textit{i+1}} \cdot \ldots \cdot \alpha_m$. Assume that $q_0 \xrightarrow{\alpha_1} q_1 \ldots \xrightarrow{\alpha_i} q_i \xrightarrow{\alpha_{\textit{i+1}}} q_{\textit{i+1}} \ldots  \xrightarrow{\alpha_m} q_m$ is the path of $l_1$ on $\textit{PQ}_s$. For each $i \leq k \leq m$, let $q'_k$ be the same as $q_k$, except that $q'_k$ maps $p$ into $\textit{item} \cdot l_k$ and $q_k$ maps $p$ into $l_k$ for some finite sequence $l_k$.

    We already know that $q_0 \xrightarrow{\alpha_1} q_1 \ldots \xrightarrow{\alpha_i} q_i$, and it is obvious that $q_i \xrightarrow{\textit{put}(\textit{itm},p)} q'_i$. Since (1) all $\textit{put}$ with priority $p$ is in $u$, (2) in $u \cdot v$, only items with priority either incomparable, or less, or equal than $p$ is removed, we can see that it is safe to add to each $q_k$ ($1 \leq k \leq m$) with a newest $\textit{itm}$ with priority $p$. Or we can say, $q'_i \xrightarrow{\alpha_{\textit{i+1}}} q'_{\textit{i+1}} \ldots \xrightarrow{\alpha_m} q'_m$ are transitions of $\textit{LTS}_e$. Therefore, we can see that $l_2 = u \cdot \textit{put}(\textit{itm},p) \cdot v \in \textit{PQ}_s$.

\item[-] If $l_1 \in \textit{PQ}_{s\neq}$ and $l_2 \xrightarrow{\textit{PQ}_3} l_1$. Then we need to prove that $l_2 \in \textit{PQ}_s$. We know that $l_1 = u \cdot v$, such that $\textit{PQ}_3(u,v)$ holds, and $l_2 = u \cdot \textit{rm}(\textit{empty}) \cdot v$.

    Assume that $u = \alpha_1 \cdot \ldots \cdot \alpha_i$ and $v = \alpha_{\textit{i+1}} \cdot \ldots \cdot \alpha_m$. Assume that $q_0 \xrightarrow{\alpha_1} q_1 \ldots \xrightarrow{\alpha_i} q_i \xrightarrow{\alpha_{\textit{i+1}}} q_{\textit{i+1}} \ldots  \xrightarrow{\alpha_m} q_m$ is the path of $l_1$ on $\textit{PQ}_s$.

    We already know that $q_0 \xrightarrow{\alpha_1} q_1 \ldots \xrightarrow{\alpha_i} q_i$. Since $\textit{matched}(u)$ holds, we can see that $q_i$ maps each element in $\mathbb{P}$ into $\epsilon$, and then $q_i \xrightarrow{\textit{rm}(\textit{empty})} q_i$. We already know that $q_i \xrightarrow{\alpha_{\textit{i+1}}} q_{\textit{i+1}} \ldots \xrightarrow{\alpha_m} q_m$. Therefore, we can see that $l_2 = u \cdot \textit{rm}(\textit{empty}) \cdot v \in \textit{PQ}_s$.
\end{itemize}

To prove that $\textit{PQ} \subseteq \textit{PQ}_s$. It is easy to see that $\textit{PQ}$ and $\textit{PQ}_s$ are both data-independent. Given $e_1 \in \textit{PQ}$, by data-independence we know that there is a data-differentiated sequential execution $e' \in \textit{PQ}$ and renaming function $f$, such that $e=f(e')$. By $\textit{PQ}_{\neq} \subseteq \textit{PQ}_{s\neq}$, we know that $e' \in \textit{PQ}_{s\neq}$. By data-independence, we know that $e \in \textit{PQ}_s$.

To prove that $\textit{PQ}_s \subseteq \textit{PQ}$, let us first prove $\textit{PQ}_{s\neq} \subseteq \textit{PQ}_{\neq}$. We show that given $l_2 \in \textit{PQ}_{s\neq}$, how to construct a sequence $l_1$, such that $l_2 \xrightarrow{R} l_1$ for some $R$, and $l_1 \in \textit{PQ}_s$. Based on this, we can decompose a sequence of $\textit{PQ}_s$ into $\epsilon$, and this process ensures that this sequence is in $\textit{PQ}$. Note that from a $l_2$ we may construct more than one $l_1$, and this does not influence the correctness of our proof.

\begin{itemize}
\setlength{\itemsep}{0.5pt}
\item[-] If $l_2$ contains $\textit{rm}(\textit{empty})$: Assume that $l_2 = u \cdot \textit{rm}(\textit{empty}) \cdot v$. It is easy to see that $\textit{matched}(u)$ holds. Let $l_1 = u \cdot v$. It is easy to see that $l_2 \xrightarrow{\textit{PQ}_3} l_1$, and $\textit{PQ}_3(u,v)$ holds.

    Assume that $u = \alpha_1 \cdot \ldots \cdot \alpha_i$ and $v = \alpha_{\textit{i+1}} \cdot \ldots \cdot \alpha_m$. Since We already know that $q_0 \xrightarrow{\alpha_1} q_1 \ldots \xrightarrow{\alpha_i} q_i \xrightarrow{\textit{rm}(\textit{empty})} q'_i \xrightarrow{\alpha_{\textit{i+1}}} q_{\textit{i+1}} \ldots  \xrightarrow{\alpha_m} q_m$ is transitions of $\textit{LTS}_e$. It is easy to see that $q_i = q'_i$, and they map each element in $\mathbb{P}$ into $\epsilon$. Then we can see that $q_0 \xrightarrow{\alpha_1} q_1 \ldots \xrightarrow{\alpha_i} q_i \xrightarrow{\alpha_{\textit{i+1}}} q_{\textit{i+1}} \ldots  \xrightarrow{\alpha_m} q_m$ is transitions of $\textit{LTS}_e$, and $l_1 \in \textit{PQ}_s$.

\item[-] If $l_2$ does not contain $\textit{rm}(\textit{empty})$, $p$ is one of maximal priority of $l_2$, and items in $l_2$ with priority $p$ are unmatched $\textit{put}$ and (possibly) matched $\textit{put}$:

    Assume that $l_2 = u \cdot \textit{put}(\textit{itm},p) \cdot v$, such that all $\textit{put}$ with priority $p$ of $u \cdot v$ is in $u$. Let $l_1 = u \cdot v$. According to construction of $\textit{LTS}_e$, we can see that $\textit{PQ}_2(u,v,p)$ holds, and $l_2 \xrightarrow{\textit{PQ}_2} l_1$.

    Assume that $u = \alpha_1 \cdot \ldots \cdot \alpha_i$ and $v = \alpha_{\textit{i+1}} \cdot \ldots \cdot \alpha_m$. We already know that $\textit{pa} = q_0 \xrightarrow{\alpha_1} q_1 \ldots \xrightarrow{\alpha_i} q_i \xrightarrow{\textit{put}(\textit{itm},p)} q_{\textit{i+}} \xrightarrow{\alpha_{\textit{i+1}}} q_{\textit{i+1}} \ldots \xrightarrow{\alpha_m} q_m$ are transitions of $\textit{LTS}_e$. For each $\textit{i+1} \leq k \leq m$, let $q'_k$ be the same as $q_k$, except that $q_k$ maps $p$ into some $\textit{itm} \cdot l_k$ for some finite sequence $l_k$, and $q'_k$ maps $p$ into $l_k$. Since (1) all $\textit{put}$ with priority $p$ of $u \cdot v$ is in $u$ and (2) $p$ is one of maximal priority of $l_2$, it is safe to remove $\textit{itm}$ without influence other transitions of $\textit{pa}$. Or we can say, $q_0 \xrightarrow{\alpha_1} q_1 \ldots \xrightarrow{\alpha_i} q_i \xrightarrow{\alpha_{\textit{i+1}}} q'_{\textit{i+1}} \ldots \xrightarrow{\alpha_m} q'_m$ are transitions of $\textit{LTS}_e$. Therefore, $l_1 \in \textit{PQ}_s$.

\item[-] If $l_2$ does not contain $\textit{rm}(\textit{empty})$, $p$ is one of maximal priority of $l_2$, and items in $l_2$ with priority $p$ are matched $\textit{put}$:

    Assume that $l_2 = u \cdot \textit{put}(\textit{itm},p) \cdot v \cdot \textit{rm}(\textit{itm}) \cdot w$, such that all $\textit{put}$ with priority $p$ of $u \cdot v \cdot w$ is in $u$. Let $l_1 = u \cdot v \cdot w$. According to construction of $\textit{LTS}_e$, we can see that $\textit{PQ}_1(u,v,w,p)$ holds, and $l_2 \xrightarrow{\textit{PQ}_1} l_1$.

    Assume that $u = \alpha_1 \cdot \ldots \cdot \alpha_i$, $v = \alpha_{\textit{i+1}} \cdot \ldots \cdot \alpha_j$ and $w = \alpha_{\textit{j+1}} \cdot \ldots \cdot \alpha_m$. We already know that $q_0 \xrightarrow{\alpha_1} q_1 \ldots \xrightarrow{\alpha_i} q_i \xrightarrow{\textit{put}(\textit{itm},\textit{pri})} q_{\textit{i+}} \xrightarrow{\alpha_{\textit{i+1}}} q_{\textit{i+1}} \ldots \xrightarrow{\alpha_j} q_j \xrightarrow{\textit{rm}(\textit{itm})} q_{\textit{j+}} \xrightarrow{\alpha_{\textit{j+1}}} q_{\textit{j+1}} \ldots \xrightarrow{\alpha_m} q_m$. For each $\textit{i+1} \leq k \leq j$, let $q'_k$ be the same as $q_k$, except that $q_k$ maps $p$ into $\textit{itm} \cdot l_k$ for some finite sequence $l_k$, and $q'_k$ maps $p$ into $l_k$. Since (1) $p$ is one of maximal priority in $l_2$, (2) $\textit{itm}$ is the newest item with priority $p$ in $l_2$, and (3) $\textit{itm}$ is not removed until $\textit{rm}(\textit{itm})$, we know that whether we keep $\textit{itm}$ or remove it will not influence transitions from $q_{\textit{i+1}}$ to $q_j$. Then we can see that $q_0 \xrightarrow{\alpha_1} q_1 \ldots \xrightarrow{\alpha_i} q_i \xrightarrow{\alpha_{\textit{i+1}}} q'_{\textit{i+1}} \ldots \xrightarrow{\alpha_j} q'_j \xrightarrow{\alpha_{\textit{j+1}}} q_{\textit{j+1}} \ldots \xrightarrow{\alpha_m} q_m$ are transitions of $\textit{LTS}_e$. Therefore, $l_1 \in \textit{PQ}_s$.
\end{itemize}

To prove that $\textit{PQ}_s \subseteq \textit{PQ}$. Given $e_1 \in \textit{PQ}_s$, by data-independence we know that there is a data-differentiated sequential execution $e' \in \textit{PQ}_s$ and renaming function $f$, such that $e=f(e')$. By $\textit{PQ}_{s\neq} \subseteq \textit{PQ}_{\neq}$, we know that $e' \in \textit{PQ}_{\neq}$. By data-independence, we know that $e \in \textit{PQ}$. \qed
\end {proof}

@@

\begin {proof}
Let $l=o_1 \cdot \ldots \cdot o_m$, and $q_0 \xrightarrow{o_1} q_1 \ldots \xrightarrow{o_m} q_m$ be the path of $l$ in $\textit{LTS}_e$. Assume that $l'$ is generated from $l$ by discarding $o_{\textit{ind1}},\ldots,o_{\textit{indn}}$. Let $D$ be the set such that $D$ contains $a$, if $\textit{put}(a,\_)$ is in $o_{\textit{ind1}},\ldots,o_{\textit{indn}}$. For each $i$, let $q'_i$ be generated from $q_i$ by erasing items in $D$.

@@

\begin {proof}
Let $l=o_1 \cdot \ldots \cdot o_m$, and $q_0 \xrightarrow{o_1} q_1 \ldots \xrightarrow{o_m} q_m$ be the path of $l$ in $\textit{LTS}_e$. Assume that $l'$ is generated from $l$ by discarding all operations $o_i$ if (1) $o_i \in O_i(l,\textit{pri})$ and (2) $i \geq k$ for a specific index $k$. Let $D$ be a set such that $a \in D$, if $\textit{put}(a,\_)$ is in $l$ and not in $l'$. For each $0 \leq i \leq m$, let $q'_i$ be generated from $q_i$ by erasing items in $D$.

@@

\begin {proof}
Let $l=o_1 \cdot \ldots \cdot o_m$, and $q_0 \xrightarrow{o_1} q_1 \ldots \xrightarrow{o_m} q_m$ be the path of $l$ in $\textit{LTS}_e$. Let $l_1 = o_1 \cdot \ldots \cdot o_n$, let $l_2 = o_{\textit{n+1}} \cdot \ldots \cdot o_m$, let $l_3 = o'_{\textit{n+1}} \cdot \ldots \cdot o'_k$, let $l_4 = o'_{\textit{k+1}} \cdot \ldots \cdot o'_m$. Let $f$ be a function, such that $f(i)=j$, if $o'_i = o_j$.

@@

\begin {proof}
Let $l=o_1 \cdot \ldots \cdot o_m$, and $q_0 \xrightarrow{o_1} q_1 \ldots \xrightarrow{o_m} q_m$ be the path of $l$ in $\textit{LTS}_e$. Let $l_1 = o'_1 \cdot \ldots \cdot o'_n$, let $l_3 = o'_{\textit{n+1}} \cdot \ldots \cdot o'_m$. Let $f$ be a function, such that $f(i)=j$, if $o'_i = o_j$. Let $D$ be the se of items which are added and not removed in $o'_1 \cdot \ldots \cdot o'_n$.

>>>>

\section{Definition of $\seqPQ$ and Proof of Lemma \ref{lemma:EPQ rules and semantics}}
\label{sec:appendix definition of seqPQ and proof of Lemma EQP rules and semantics}

@@

Let us model priority queue as an LTS $\textit{PQ} = (Q,\Sigma,\rightarrow,q_0)$ as follows:

@@

A path of an LTS is a finite transition sequence $q_0\xrightarrow{\beta_1}q_1\overset{\beta_2}{\longrightarrow}\ldots\overset{\beta_k}{\longrightarrow}q_k$ for $k\geq 0$, where $q_0$ is the initial state of the LTS. A trace of an LTS is a finite sequence $\beta_1 \cdot \beta_2 \cdot \ldots \cdot \beta_k$, where $k \geq 0$ if there exists a path $q_0\overset{\beta_1}{\longrightarrow}q_1\overset{\beta_2}{\longrightarrow}\ldots\overset{\beta_k}{\longrightarrow}q_k$ of the LTS. Let $\seqPQ$ be the set of traces of $\textit{PQ}$. The following lemma states that $\seqPQ$ is indeed the set of sequences obtained by renaming sequences accepted by $\textit{Check-PQ-Seq}$.

$\textit{Check-PQ-Seq}(e)=\mathsf{true}$ iff $e\in \seqPQ$, for every data-differentiated sequential execution $e$..

@@

Let $\textit{SeqPQ}_f$ be the set of data-differentiated sequences, such that $e \in \textit{SeqPQ}_f$, if $\textit{Check-PQ-Seq}(e)=\mathsf{true}$. We need to prove that $\textit{SeqPQ}_f = \seqPQ_{\neq}$. Given $\Gamma\in \{\mathsf{EmptyRemove}, \mathsf{UnmatchedMaxPriority}, \mathsf{MatchedMaxPriority}\}$, let us use $l_2 \xrightarrow{\Gamma} l_1$ to mean that when we use $\textit{Check-PQ-Seq}$ to check $l_2$, we choose the branch of $\mathsf{Has\text{-}\Gamma}$ and finally recursively call $\textit{Check-PQ-Seq}$ to check $l_1$.

We prove $\textit{SeqPQ}_f \subseteq \seqPQ_{\neq}$ by induction.

\begin{itemize}
\setlength{\itemsep}{0.5pt}
\item[-] It is obvious that $\epsilon \in \seqPQ$.

\item[-] If $l_1 \in \seqPQ_{\neq}$ and $l_2 \xrightarrow{\mathsf{MatchedMaxPriority}} l_1$. Then we need to prove that $l_2 \in \seqPQ$. We know that $l_1 = u \cdot v \cdot w$, such that $\mathsf{MatchedMaxPriority\text{-}Seq}(l_2,x)$ holds and $l_2 = u \cdot \textit{put}(x,p) \cdot v \cdot \textit{rm}(x) \cdot w$.

    Assume that $u = \alpha_1 \cdot \ldots \cdot \alpha_i$, $v = \alpha_{\textit{i+1}} \cdot \ldots \cdot \alpha_j$ and $w = \alpha_{\textit{j+1}} \cdot \ldots \cdot \alpha_m$. Assume that $q_0 \xrightarrow{\alpha_1} q_1 \ldots \xrightarrow{\alpha_i} q_i \xrightarrow{\alpha_{\textit{i+1}}} q_{\textit{i+1}} \ldots  \xrightarrow{\alpha_j} q_j \xrightarrow{\alpha_{\textit{j+1}}} q_{\textit{j+1}} \ldots \xrightarrow{\alpha_m} q_m$ is the path of $l_1$ on $\textit{PQ}$. For each $i \leq k \leq j$, let $q'_k$ be the same as $q_k$, except that $q'_k$ maps $p$ into $\textit{item} \cdot l_k$ and $q_k$ maps $\textit{pri}$ into $l_k$ for some finite sequence $l_k$.

    We already know that $q_0 \xrightarrow{\alpha_1} q_1 \ldots \xrightarrow{\alpha_i} q_i$, and it is obvious that $q_i \xrightarrow{\textit{put}(x,p)} q'_i$. Since (1) all $\textit{put}$ with priority $p$ is in $u$, and (2) in $u \cdot v$, only items with priority either incomparable, or less, or equal than $p$ is removed, we can see that it is safe to add to each $q_k$ ($1 \leq k \leq j$) with a newest $x$ with priority $p$. Or we can say, $q'_i \xrightarrow{\alpha_{\textit{i+1}}} q'_{\textit{i+1}} \ldots \xrightarrow{\alpha_j} q'_j$ are transitions of $\textit{PQ}$. Since $\textit{matched}_{\prec}(u \cdot v,p)$ holds, we can see that $q_j$ maps each priority that is smaller than $p$ into $\epsilon$ and maps $p$ into $\epsilon$, and $q'_j$ maps each priority that is smaller than $p$ into $\epsilon$ and maps $p$ into $x$. Then, we can see that $q'_j \xrightarrow{\textit{rm}(x)} q_j$. We already know that that $q_j \xrightarrow{\alpha_{\textit{j+1}}} q_{\textit{j+1}} \ldots \xrightarrow{\alpha_m} q_m$. Therefore, we can see that $l_2 = u \cdot \textit{put}(x,p) \cdot v \cdot \textit{rm}(x) \in \seqPQ$.

\item[-] If $l_1 \in \seqPQ_{\neq}$ and $l_2 \xrightarrow{\mathsf{UnmatchedMaxPriority}} l_1$. Then we need to prove that $l_2 \in \seqPQ$. We know that $l_1 = u \cdot v$, such that $\mathsf{UnmatchedMaxPriority\text{-}Seq}(l_2,x)$ holds and $l_2 = u \cdot \textit{put}(x,p) \cdot v$.

    Assume that $u = \alpha_1 \cdot \ldots \cdot \alpha_i$ and $v = \alpha_{\textit{i+1}} \cdot \ldots \cdot \alpha_m$. Assume that $q_0 \xrightarrow{\alpha_1} q_1 \ldots \xrightarrow{\alpha_i} q_i \xrightarrow{\alpha_{\textit{i+1}}} q_{\textit{i+1}} \ldots  \xrightarrow{\alpha_m} q_m$ is the path of $l_1$ on $\textit{PQ}$. For each $i \leq k \leq m$, let $q'_k$ be the same as $q_k$, except that $q'_k$ maps $p$ into $\textit{item} \cdot l_k$ and $q_k$ maps $p$ into $l_k$ for some finite sequence $l_k$.

    We already know that $q_0 \xrightarrow{\alpha_1} q_1 \ldots \xrightarrow{\alpha_i} q_i$, and it is obvious that $q_i \xrightarrow{\textit{put}(x,p)} q'_i$. Since (1) all $\textit{put}$ with priority $p$ is in $u$, (2) in $u \cdot v$, only items with priority either incomparable, or less, or equal than $p$ is removed, we can see that it is safe to add to each $q_k$ ($1 \leq k \leq m$) with a newest $x$ with priority $p$. Or we can say, $q'_i \xrightarrow{\alpha_{\textit{i+1}}} q'_{\textit{i+1}} \ldots \xrightarrow{\alpha_m} q'_m$ are transitions of $\textit{PQ}$. Therefore, we can see that $l_2 = u \cdot \textit{put}(x,p) \cdot v \in \seqPQ$.

\item[-] If $l_1 \in \seqPQ_{\neq}$ and $l_2 \xrightarrow{\mathsf{EmptyRemove}} l_1$. Then we need to prove that $l_2 \in \seqPQ$. We know that $l_1 = u \cdot v$, such that $\mathsf{EmptyRemove\text{-}Seq}(l_2,o)$ holds, and $l_2 = u \cdot \textit{rm}(\textit{empty}) \cdot v$ with $o=\textit{rm}(\textit{empty})$.

    Assume that $u = \alpha_1 \cdot \ldots \cdot \alpha_i$ and $v = \alpha_{\textit{i+1}} \cdot \ldots \cdot \alpha_m$. Assume that $q_0 \xrightarrow{\alpha_1} q_1 \ldots \xrightarrow{\alpha_i} q_i \xrightarrow{\alpha_{\textit{i+1}}} q_{\textit{i+1}} \ldots  \xrightarrow{\alpha_m} q_m$ is the path of $l_1$ on $\textit{PQ}$.

    We already know that $q_0 \xrightarrow{\alpha_1} q_1 \ldots \xrightarrow{\alpha_i} q_i$. Since $\textit{matched}(u)$ holds, we can see that $q_i$ maps each element in $\mathbb{P}$ into $\epsilon$, and then $q_i \xrightarrow{\textit{rm}(\textit{empty})} q_i$. We already know that $q_i \xrightarrow{\alpha_{\textit{i+1}}} q_{\textit{i+1}} \ldots \xrightarrow{\alpha_m} q_m$. Therefore, we can see that $l_2 = u \cdot \textit{rm}(\textit{empty}) \cdot v \in \seqPQ$.
\end{itemize}

To prove that $\seqPQ_{\neq} \subseteq \textit{SeqPQ}_f$, we show that given $l_2 \in \seqPQ_{\neq}$, how to construct a sequence $l_1$, such that $l_2 \xrightarrow{\Gamma} l_1$ for some $\Gamma$, and $l_1 \in \seqPQ$. Based on this, we can decompose a sequence of $\seqPQ$ into $\epsilon$, and this process ensures that this sequence is in $\textit{SeqPQ}_f$. Note that from a $l_2$ we may construct more than one $l_1$, and this does not influence the correctness of our proof.

\begin{itemize}
\setlength{\itemsep}{0.5pt}
\item[-] If $\mathsf{Has\text{-}EmptyRemoves}(l_2)$: Assume that $l_2 = u \cdot \textit{rm}(\textit{empty}) \cdot v$. It is easy to see that $\textit{matched}(u)$ holds. Let $l_1 = u \cdot v$. It is easy to see that $l_2 \xrightarrow{\mathsf{EmptyRemove}} l_1$, and $\mathsf{UnmatchedMaxPriority\text{-}Seq}(l_2,o)$ holds for some $o=\textit{rm}(\textit{empty})$.

    Assume that $u = \alpha_1 \cdot \ldots \cdot \alpha_i$ and $v = \alpha_{\textit{i+1}} \cdot \ldots \cdot \alpha_m$. Since We already know that $q_0 \xrightarrow{\alpha_1} q_1 \ldots \xrightarrow{\alpha_i} q_i \xrightarrow{\textit{rm}(\textit{empty})} q'_i \xrightarrow{\alpha_{\textit{i+1}}} q_{\textit{i+1}} \ldots  \xrightarrow{\alpha_m} q_m$ is transitions of $\textit{PQ}$. It is easy to see that $q_i = q'_i$, and they map each element in $\mathbb{P}$ into $\epsilon$. Then we can see that $q_0 \xrightarrow{\alpha_1} q_1 \ldots \xrightarrow{\alpha_i} q_i \xrightarrow{\alpha_{\textit{i+1}}} q_{\textit{i+1}} \ldots  \xrightarrow{\alpha_m} q_m$ is transitions of $\textit{PQ}$, and $l_1 \in \seqPQ$.

\item[-] If $\mathsf{Has\text{-}UnmatchedMaxPriority}(l_2)$: Assume that $l_2 = u \cdot \textit{put}(x,p) \cdot v$, such that all $\textit{put}$ with priority $p$ of $u \cdot v$ is in $u$. Let $l_1 = u \cdot v$. According to construction of $\textit{PQ}$, we can see that $\mathsf{UnmatchedMaxPriority\text{-}Seq}(l_2,x)$ holds, and $l_2 \xrightarrow{\mathsf{UnmatchedMaxPriority}} l_1$.

    Assume that $u = \alpha_1 \cdot \ldots \cdot \alpha_i$ and $v = \alpha_{\textit{i+1}} \cdot \ldots \cdot \alpha_m$. We already know that $\textit{pa} = q_0 \xrightarrow{\alpha_1} q_1 \ldots \xrightarrow{\alpha_i} q_i \xrightarrow{\textit{put}(x,p)} q_{\textit{i+}} \xrightarrow{\alpha_{\textit{i+1}}} q_{\textit{i+1}} \ldots \xrightarrow{\alpha_m} q_m$ are transitions of $\textit{PQ}$. For each $\textit{i+1} \leq k \leq m$, let $q'_k$ be the same as $q_k$, except that $q_k$ maps $p$ into some $x \cdot l_k$ for some finite sequence $l_k$, and $q'_k$ maps $p$ into $l_k$. Since (1) all $\textit{put}$ with priority $p$ of $u \cdot v$ is in $u$ and (2) $p$ is one of maximal priority of $l_2$, it is safe to remove $x$ without influence other transitions of $\textit{pa}$. Or we can say, $q_0 \xrightarrow{\alpha_1} q_1 \ldots \xrightarrow{\alpha_i} q_i \xrightarrow{\alpha_{\textit{i+1}}} q'_{\textit{i+1}} \ldots \xrightarrow{\alpha_m} q'_m$ are transitions of $\textit{PQ}$. Therefore, $l_1 \in \seqPQ$.

\item[-] If $\mathsf{Has\text{-}MatchedMaxPriority}(l_2)$: Assume that $l_2 = u \cdot \textit{put}(x,p) \cdot v \cdot \textit{rm}(x) \cdot w$, such that all $\textit{put}$ with priority $p$ of $u \cdot v \cdot w$ is in $u$. Let $l_1 = u \cdot v \cdot w$. According to construction of $\textit{PQ}$, we can see that $\mathsf{MatchedMaxPriority\text{-}Seq}(l_2,x)$ holds, and $l_2 \xrightarrow{\mathsf{MatchedMaxPriority}} l_1$.

    Assume that $u = \alpha_1 \cdot \ldots \cdot \alpha_i$, $v = \alpha_{\textit{i+1}} \cdot \ldots \cdot \alpha_j$ and $w = \alpha_{\textit{j+1}} \cdot \ldots \cdot \alpha_m$. We already know that $q_0 \xrightarrow{\alpha_1} q_1 \ldots \xrightarrow{\alpha_i} q_i \xrightarrow{\textit{put}(x,p)} q_{\textit{i+}} \xrightarrow{\alpha_{\textit{i+1}}} q_{\textit{i+1}} \ldots \xrightarrow{\alpha_j} q_j \xrightarrow{\textit{rm}(x)} q_{\textit{j+}} \xrightarrow{\alpha_{\textit{j+1}}} q_{\textit{j+1}} \ldots \xrightarrow{\alpha_m} q_m$. For each $\textit{i+1} \leq k \leq j$, let $q'_k$ be the same as $q_k$, except that $q_k$ maps $p$ into $x \cdot l_k$ for some finite sequence $l_k$, and $q'_k$ maps $p$ into $l_k$. Since (1) $p$ is one of maximal priority in $l_2$, (2) $x$ is the newest item with priority $p$ in $l_2$, and (3) $x$ is not removed until $\textit{rm}(x)$, we know that whether we keep $x$ or remove it will not influence transitions from $q_{\textit{i+1}}$ to $q_j$. Then we can see that $q_0 \xrightarrow{\alpha_1} q_1 \ldots \xrightarrow{\alpha_i} q_i \xrightarrow{\alpha_{\textit{i+1}}} q'_{\textit{i+1}} \ldots \xrightarrow{\alpha_j} q'_j \xrightarrow{\alpha_{\textit{j+1}}} q_{\textit{j+1}} \ldots \xrightarrow{\alpha_m} q_m$ are transitions of $\textit{PQ}$. Therefore, $l_1 \in \seqPQ$.
\end{itemize}

@@

\begin {proof}
Let $l=o_1 \cdot \ldots \cdot o_m$, and $q_0 \xrightarrow{o_1} q_1 \ldots \xrightarrow{o_m} q_m$ be the path of $l$ in $\textit{PQ}$. Assume that $l'$ is generated from $l$ by discarding $o_{\textit{ind1}},\ldots,o_{\textit{indn}}$. Let $D$ be the set such that $D$ contains $a$, if $\textit{put}(a,\_)$ is in $o_{\textit{ind1}},\ldots,o_{\textit{indn}}$. For each $i$, let $q'_i$ be generated from $q_i$ by erasing items in $D$.

@@

\begin {proof}
Let $l=o_1 \cdot \ldots \cdot o_m$, and $q_0 \xrightarrow{o_1} q_1 \ldots \xrightarrow{o_m} q_m$ be the path of $l$ in $\textit{PQ}$. Assume that $l'$ is generated from $l$ by discarding all operations $o_i$ if (1) $o_i \in O_i(l,\textit{pri})$ and (2) $i \geq k$ for a specific index $k$. Let $D$ be a set such that $a \in D$, if $\textit{put}(a,\_)$ is in $l$ and not in $l'$. For each $0 \leq i \leq m$, let $q'_i$ be generated from $q_i$ by erasing items in $D$.

@@

\begin {proof}
Let $l=o_1 \cdot \ldots \cdot o_m$, and $q_0 \xrightarrow{o_1} q_1 \ldots \xrightarrow{o_m} q_m$ be the path of $l$ in $\textit{PQ}$. Let $l_1 = o_1 \cdot \ldots \cdot o_n$, let $l_2 = o_{\textit{n+1}} \cdot \ldots \cdot o_m$, let $l_3 = o'_{\textit{n+1}} \cdot \ldots \cdot o'_k$, let $l_4 = o'_{\textit{k+1}} \cdot \ldots \cdot o'_m$. Let $f$ be a function, such that $f(i)=j$, if $o'_i = o_j$.

@@

\begin {proof}
Let $l=o_1 \cdot \ldots \cdot o_m$, and $q_0 \xrightarrow{o_1} q_1 \ldots \xrightarrow{o_m} q_m$ be the path of $l$ in $\textit{PQ}$. Let $l_1 = o'_1 \cdot \ldots \cdot o'_n$, let $l_3 = o'_{\textit{n+1}} \cdot \ldots \cdot o'_m$. Let $f$ be a function, such that $f(i)=j$, if $o'_i = o_j$. Let $D$ be the se of items which are added and not removed in $o'_1 \cdot \ldots \cdot o'_n$.
